Making Sequential Programs Deterministic

### 2019-03-24 introduction.tex
intro todo

Other researchers have also recognized the importance of this problem.
Previous work in program analysis for nondeterminism has focused on unsound dynamic
approaches that identify flaky test cases.
NonDex~\cite{nondex} is a tool that manually\todo{This is confusing:  the
  tool can't manually identify.  Do you mean that the developers manually
  identified, then the tool uses those models?}
identifies methods in the JDK that have nondeterministic specifications, builds models for
these methods that behave nondeterministically, and  use a modified JVM that runs the test suite multiple times.
Diverging test results in this setting indicate a flaky test. DeFlaker~\cite{deflaker} looks at a range of commit versions
of a code, and marks a test as flaky if it doesn't execute any modified code but still fails in the newer version. These techniques
have been able to identify issues in real-world programs, some of which
have been fixed by the developers. We believe that identifying and
resolving nondeterminism
at an earlier phase in the software development lifecycle would be greatly beneficial to
developers.

>>>>

Other researchers have also recognized the importance of this problem.
Previous work in program analysis for nondeterminism has focused on unsound dynamic
approaches that identify flaky test cases.
The authors of~\cite{nondex} manually identify methods in the JDK that have nondeterministic specifications and build models for
these methods. They  modified that JVM so that it runs the test suite multiple times.
%NonDex~\cite{nondex} is a tool that manually\todo{This is confusing:  the
%  tool can't manually identify.  Do you mean that the developers manually
%  identified, then the tool uses those models?}
%identifies 
Diverging test results in this setting indicate a flaky test. DeFlaker~\cite{deflaker} looks at a range of commit versions
of a code, and marks a test as flaky if it doesn't execute any modified code but still fails in the newer version. These techniques
have been able to identify issues in real-world programs, some of which
have been fixed by the developers. We believe that identifying and
resolving nondeterminism
at an earlier phase in the software development lifecycle would be greatly beneficial to
developers.
